% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
 
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yuchen Dong}

% {E-mail}{mobilephone}{homepage}
\contactInfo{dongyc\_nju@163.com}{(+86) 151-9590-7609}{http://github.com/tavaresdong}
% {E-mail}{mobilephone}
%\basicContactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}
 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Nanjing University}, Nanjing, China}{2013 -- 2016}
\textit{Master student} in Computer Science and Technology.
\datedsubsection{\textbf{Nanjing University}, Nanjing, China}{2008 -- 2013}
\textit{B.S.} in Computer Science and Technology.
\textit one year sick leave.

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Morgan Stanley} Shanghai, China}{2016 -- Present}
\role{C++ Developer}{Team: E-Trading infrastructure}
Developing core trading infrastracture
\begin{itemize}
  \item Content pub/sub system integration with JSON/GPB.
  \item Fix message library development, performance tuning and message diagnostic tool development.
  \item Event-driven trading infrastructure development.
  \item High availability solution development based on multicast and TCP.
\end{itemize}

\datedsubsection{\textbf{Alibaba Inc.}}{June. 2015 -- Sept. 2015}
\role{C++ Developer}{Team: Searching BU}
Developing product score ranking service. Implement ranking service for query engine.

\datedsubsection{\textbf{Accumulator: A Program Analyzer}}{June. 2015 -- Sept. 2015}
\role{Developer}{Master research project}
Developing Java program analyzer based on eclipse jdt and
antlr, applying verification techniques like theorem proving and data-flow analysis.

\datedsubsection{\textbf{oplib}}{June. 2015 -- present}
\role{Developer}{Individual project}
Individual project: a libraries developed for fun at
github.com/tavaresdong/oplib.git
\begin{itemize}
  \item a Tiny STL container library including vector/list/set/map/unordered\_map/unorderd\_set and heap, trie. supporting C++11/14 features.
  \item A reactor-pattern network library mimicing muduo, applying one-loop per thread and multithreaded server model.
\end{itemize}

\section{\faCogs\ Skills and Interests}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C++ > C > Python = shell = Java = Go
  \item Platform: Linux System Programming
  \item Interests: Linux Network Programming, Multithreaded Programming, Redis, SQL, Go, Distributed sytem
\end{itemize}

\section{\faHeartO\ Major Honors and Awards}
\datedline{National Scholarship }{Sept. 2010}
\datedline{Nanjing University People's scholarship level 1}{Sept. 2011}
\datedline{Huawei Scholarship}{Sept. 2012}
\datedline{Morgan Stanley new trainee guru award}{Nov. 2016}

\end{document}
